Molecular dynamics simulation of synchronization of a driven particle

### 2021-05-05 manuscript/manuscript_ajp_version4b.tex
final version - includes problem 6

To explore the possible hopping patterns,
we sweep through a range of values of $F_{\rm dc}$ for fixed $F_{\rm ac}$ and $A_p$.
In Fig.~\ref{fig:3_sweep_vyFDC} 
we increase $F_{\rm dc}$ in increments of $0.001\,F_0$,
and 
measure the average velocity $\langle v_y \rangle $ 
as a function of $F_{\rm dc}$.
We also perform the sweep for a non-oscillatory drive $F_{\rm ac} = 0$.
With no oscillating component of the driving force,
  the force-velocity relation increases monotonically 
  above the depinning threshold $F_c$ such that
  \begin{equation}
    \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta},
  \end{equation}
  where the power $\beta$ varies with the
  type of phase transition and 
  %can
  may 
  be used to identify the universality class.\cite{Reichhardt2017} 
  The critical force $F_c$ is equal to the maximum substrate force
  $A_p$.
  % [xx would be good to follow up on your mention of universality class in a problem. The exponent beta is usually associated with the decrease of the order parameter, not a divergence xx]
  %DM - in my experience, we use beta for this parameter.  For example
  %Dynamic regimes for driven colloidal particles on a periodic substrate at commensurate and incommensurate fillings D McDermott, J Amelang, CJO Reichhardt, C Reichhardt, Physical Review E 88 (6), 062301

@@

   \noindent
   With no oscillating component of the driving force,
  the force-velocity relation increases monotonically 
  above the depinning threshold $F_c$ such that
  \begin{equation}
    \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta},
  \end{equation}
  where the power $\beta$ varies with the
  type of phase transition and 
  %can
  may 
  be used to identify the universality class.\cite{Reichhardt2017} 
  The critical force $F_c$ is equal to the maximum substrate force
  $A_p$.
   % [xx would be good to follow up on your mention of universality class in a problem. The exponent beta is usually associated with the decrease of the order parameter, not a divergence xx]
  %DM - in my experience, we use beta for this parameter.  For example
  %Dynamic regimes for driven colloidal particles on a periodic substrate at commensurate and incommensurate fillings D McDermott, J Amelang, CJO Reichhardt, C Reichhardt, Physical Review E 88 (6), 062301

>>>>

To explore the possible hopping patterns,
we sweep through a range of values of $F_{\rm dc}$ for fixed $F_{\rm ac}$ and $A_p$.
In Fig.~\ref{fig:3_sweep_vyFDC} 
we increase $F_{\rm dc}$ in increments of $0.001\,F_0$,
and 
measure the average velocity $\langle v_y \rangle $ 
as a function of $F_{\rm dc}$.
We also perform the sweep for a non-oscillatory drive $F_{\rm ac} = 0$.
With no oscillating component of the driving force,
  the force-velocity relation increases monotonically 
  above the depinning threshold $F_c$ such that
  \begin{equation}
    \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta},
  \end{equation}
  where the power $\beta$ varies with the
  type of phase transition and 
  %can
  may 
  be used to identify the universality class.\cite{Reichhardt2017} 
  The critical force $F_c$ is equal to the maximum substrate force
  $A_p$.
  %DM ADD
  We demonstrate how to fit our data to this model in Problem~\ref{ex:critical}.
  %DM end
  % [xx would be good to follow up on your mention of universality class in a problem. The exponent beta is usually associated with the decrease of the order parameter, not a divergence xx]
  %DM - in my experience, we use beta for this parameter.  For example
  %Dynamic regimes for driven colloidal particles on a periodic substrate at commensurate and incommensurate fillings D McDermott, J Amelang, CJO Reichhardt, C Reichhardt, Physical Review E 88 (6), 062301

@@

   \noindent
   In Fig.~\ref{fig:3_sweep_vyFDC}
   we show the force-velocity relation when
   the driving force has 
   no oscillating component.
   The data can be fit with a model 
   \begin{equation}
     \langle v_y \rangle \propto (F_{\rm dc}-F_c)^{-\beta},
   \end{equation}
   where
   the critical force is $F_c$ and 
   the power $\beta$ varies with the
   type of phase transition.
   For elastic depinning, a
   typical value of $\beta$ is
   approximately $\beta = 2/3$.\cite{Reichhardt2017}

   Given the data generated in 
   a non-oscillatory drive $F_{\rm ac} = 0$,
   fit the data and find the critical exponent $\beta$.
   The Python SciPy optimize package has curve fit routine
   suitable for this purpose.  
   %For the data in Fig.~\ref{fig:3_sweep_vyFDC}, 
   %we obtained $\beta = 0.625 \pm 0.003$ 
   %and $F_c = 0.0980 \pm 0.0001$.
   %is equal to the maximum substrate force
   %$A_p = 0.1$.
   Explore how $\beta$ and $F_c$ vary as $A_p$
   is tuned to higher and lower values.
